Photovoltaic System Reconfiguration Strategy For Mismatch Condition\\ {\footnotesize \textsuperscript{}}

### 2018-09-14 main.tex
Updates from ShareLaTeX
grammar check finished

\begin{IEEEkeywords}
  Photovoltaic system, mismathed power loss, reconfiguration, dynamical reconfiguration.
\end{IEEEkeywords}

@@

Recently, as practical solutions, reconfiguration in PV panels have been investigated \cite{b5}\cite{b10}. One PV panel typically has two (plus and minus) terminals, and a PV array is configured by connecting PV panels in series and/or parallel. Such a configuration is also realized using a switch among PV panels, and reconfigurations in PV panel level can be regarded as  practical solutions. However, the reconfiguration in PV panel level is more difficult than that in PV cell level. PV modules in the same PV panel can be individually bypassed by bypass diodes when some mismatch condition occurs, and it causes multiple maximal power points (MPPs) for one PV panel.

@@

%All the panels in PV array have the same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify voltage and current values on different maximum power point by index \textit{n}. Those parameters can be directly estimated by the prosess provided in\cite{b7}.

@@

Orozco-Gutierrez et al. further proposed a Fast reconfiguration algorithm to optimize power generation by reconfiguring the connection of PV panels \cite{b10}, where the online monitoring \cite{b6} and the power estimation \cite{b7} are utilized. In the method in \cite{b10}, first, close values of fingerprints from monitoring of PV panels are grouped with some representative values, and then possible combinations of reconfiguration are enumerated. Their power values are estimated by \cite{b7} along with careful estimation of possible errors. The method presented a simplify feasibility check and obtains estimated power values for all the possible connections for representative values with some error rate \textit{err}, and then select configurations within \textit{err} difference from the largest estimated value as candidates of the optical configurations.

@@

To assign panels in the right string, following steps are required:
\begin{enumerate} [(1)]
\item Select panels in Panel Selection Order Table. The detail explanation are described next pargraph.\label{step1}
\item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. The replacement will following servious priorities.
  %% As the example of string current on 2A, selected panels are panel P1 and P5, these panels contain modules are equal to next unselect panel P4. Then swap (P1, P5) and P4, release P1 and P5.
  \label{replace}
  %% \subitem  Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{three} panels each contain 1 working module ($m_p(i)$ = 1).
  %% \subitem Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{one} panel contain 1 working module ($m_p(i)$ = 1) and \textbf{one} contain 2 working modules ($m_p(i)$ = 2).
  %% \subitem Swap a panel contain 2 working modules ($m_p(i)$ = 2) to \textbf{two} panels each contain 1 working module ($m_p(i)$ = 1).
%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement in \ref{feasPro} equation (\ref{feas}).
% and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
\item If there remain any unselect panel, assign unselect panel to a string with minimum length. 
\end{enumerate}
\vspace{5.7cm}

>>>>

\begin{IEEEkeywords}
  Photovoltaic system, mismatched power loss, reconfiguration, dynamical reconfiguration.
\end{IEEEkeywords}

@@

Recently, as practical solutions, reconfiguration in PV panels have been investigated \cite{b5}\cite{b10}. One PV panel typically has two (plus and minus) terminals, and a PV array is configured by connecting PV panels in series and/or parallel. Such a configuration is also realized using a switch among PV panels, and re-configurations in PV panel level can be regarded as  practical solutions. However, the reconfiguration in PV panel level is more difficult than that in PV cell level. PV modules in the same PV panel can be individually bypassed by bypass diodes when some mismatch condition occurs, and it causes multiple maximal power points (MPPs) for one PV panel.

@@

%All the panels in PV array have the same number (\textit{N}) of modules. For particular module, using (\textit{$V_{mpp_n}$, $I_{mpp_n}$}) to identify voltage and current values on different maximum power point by index \textit{n}. Those parameters can be directly estimated by the process provided in\cite{b7}.

@@

Orozco-Gutierrez et al. further proposed a Fast reconfiguration algorithm to optimize power generation by re-configuring the connection of PV panels \cite{b10}, where the online monitoring \cite{b6} and the power estimation \cite{b7} are utilized. In the method in \cite{b10}, first, close values of fingerprints from monitoring of PV panels are grouped with some representative values, and then possible combinations of reconfiguration are enumerated. Their power values are estimated by \cite{b7} along with careful estimation of possible errors. The method presented a simplify feasibility check and obtains estimated power values for all the possible connections for representative values with some error rate \textit{err}, and then select configurations within \textit{err} difference from the largest estimated value as candidates of the optical configurations.

@@

To assign panels in the right string, following steps are required:
\begin{enumerate} [(1)]
\item Select panels in Panel Selection Order Table. The detail explanation are described next paragraph.\label{step1}
\item If the element in Table is 0, release corresponding panel, $m_p(i)$ = 0.
\item Replace selected panels if summations of selected panels' contain modules are equal to unselect panel. The replacement will following several priorities.
  %% As the example of string current on 2A, selected panels are panel P1 and P5, these panels contain modules are equal to next unselect panel P4. Then swap (P1, P5) and P4, release P1 and P5.
  \label{replace}
  %% \subitem  Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{three} panels each contain 1 working module ($m_p(i)$ = 1).
  %% \subitem Swap a panel contain 3 working modules ($m_p(i)$ = 3) to \textbf{one} panel contain 1 working module ($m_p(i)$ = 1) and \textbf{one} contain 2 working modules ($m_p(i)$ = 2).
  %% \subitem Swap a panel contain 2 working modules ($m_p(i)$ = 2) to \textbf{two} panels each contain 1 working module ($m_p(i)$ = 1).
%\item At each replacement, mark swapped unselect panel as fixed. Fixed panel  
\item If replacement approved, step \ref{replace} will be repeated till summations of selected panel contain modules are large or equal to \textit{$Q_{M_n}$}.
\item Otherwise, none of the replacement will be approved. Evaluate selected panels with feasibility requirement in \ref{feasPro} equation (\ref{feas}).
% and compare selected modules with the requirement of \textit{$Q_{M_n}$}.
\item If there remain any unselect panel, assign unselect panel to a string with minimum length. 
\end{enumerate}
\vspace{5.7cm}
